Toward Centrally Programming Distributed Control Planes

### 2016-01-22 paper/expressiveness.tex
Added future work section

The argument for stability comes from the path suffix condition.

>>>>

The reduction is via the well-known No-Dispute-Wheel condition~\ref{bib:todo}. If a set of BGP configurations do not have a dispute wheel, then they will converge to their best routes. Any BGP policy with a dispute wheel will not satisfy the failure safety condition in Section~\ref{sec:compilation}. Assume that there is a dispute wheel. Then that means each node $u_i$ in the dispute wheel prefers to go through
